\recipient{To Mozilla}{}

\date{August 6, 2021}
\opening{Dear Madam, Sir,}

\closing{I have enclosed my CV for your consideration and I'm looking forward to hear from you for an interview. I remain at your disposal if you need more information about my profile.}

\enclosure{curriculum vit\ae{}}

\makelettertitle

I am reaching to you about your open position of \textbf{Senior Front-End Developer} with a strong excitement. Firefox was my first open door to the marvelous world wide web when I was a teenager. Your company had a huge impact on my current position. Near the Normandie's landscape, I stayed at home during the rainy days and I learned HTML with your old NVU tool. The web philosophy diffused by your corporation inspired me until now: I will always be the guy that argues for the importance of the privacy on the web and I often promotes tools that follows the open and free philosophies. I'm always following news from Mozilla and I'm still excited with your innovations like Rust!

Instead of being a strong Java developer as I was predestined by my studies in corporate engineering, I found more interresting challenges in the web development because I could work on both design and architectural aestetics. The web developpement stimulates my creativity and I am always happy when I can work hand-by-hand with UX and UI designers. I love thinking that my mother could use my work and made its life easier without frustration. I want my applications to be strongly functionnal, ergonomic for the end user, enough well-designed that it won't make maintenance unpleasant for my successors and at least visually appealing for everyone. On the other hand, my studies in Back-End solutions pushed my curiosity to the Rust language: I have tried for many years to learn and build a personnal project with it. This brings me the taste for experimenting new languages.

I want to contribute to your project with my Javascript skills. I used to work asynchronously with my team since the pandemic and I am ready to work with a distributed team! During these times, I rewrite completly our main application with ReactJS in order to reduce our technical debt: the old Javascript frameworks made the maintenance tricky for us and for potential new contributors. Moreover, the Society for Arts and Technology leads our team to prototype innovating tools in order to reduce the distances between the communities in the Quebec province: we stabilized the telepresence tool Scenic, we prototype a telepresence tool for the libraries with Bibliolab and we prototype a haptic floor technology for new kind of artistic performances. The fact that these tools are dedicated to communities is important for me: I produce code for every people. Regardless to my respect for the open and free projects, I learned how to be mellow by taking account that we need to balance our focus between helping businesses and contributing to community projects.

This statement drives my enrollement to the Society for Arts and Technology and it leads this letter. I am convinced that we can fight the future humain challenges by sharing our skills and by making accessible products for people. I feel this opinion was teached by my use of Firefox everyday and I assume that working for you will be my better retribution for this lesson.

\textit{Je parle aussi très bien français et j'aime beaucoup les environnements multiculturels. Merci pour votre attention.}

\makeletterclosing
