\recipient{Autodesk Canada Co.}{10 rue Duke\\
Montreal, Quebec, H3C 2L7\\
Canada}

\date{\today}
\opening{Madame, Monsieur,}
\closing{I have enclosed my CV for your consideration and I look forward to hearing from you shortly for an interview.}
\enclosure[Ci-joint]{curriculum vit\ae{}}

\makelettertitle

I am applying for internship in your firm in order to acquire experience in software development, testing, and engineering knowledge. I know Autodesk for all your powerful tools for digital creation. I studied the possibilities brought by \textit{AutoCAD} during an exercise in project management which was devoted to the planning the better software solution for a customer who worked in marketing. Furthermore, I know \textit{Maya} as a very used software for video games and for animated movies.

Currently, my three years of study in Computer Science engineering at ISIMA (College of Engineering in Computer Science, Modelling and Applications) and at the University of Québec in Chicoutimi led me to get interested in the \textbf{applications programming in Java and C++ and architectures of applications}. I have a sturdy luggage in software development and I hope improving my skills in your company. I had a course dedicated to the progress of a game engine and we got an important culture on the foundations of a game engine concerning the graphics, the animations, and all the main features of a full game engine. In addition, I made several projects in C++, C\# and Java, and I enjoyed working on my code in order to make it as comprehensive as possible. My previous internship in Infineon made me work on a C\# application and I needed to manage all the UI development, the logic of the application and the maintainability for the next teams on the project. I worked on an Android project aimed to allow people to find recipes directly from a picture of their fridge and I enjoyed making all the software architecture. Eventually, all my homemade work is done on OSX and I use for work on the Apple development platform too.

My studies in the Software Engineering and Information Systems Division of ISIMA make me apt to work with your company in the development of applications. As you see in my curriculum vit\ae{}, I am applying for a 6-month internship because I need it in order to validate my diploma but I stay very flexible concerning the duration of the internship.

\makeletterclosing
