\recipient{Axon-ID}{410, St-Nicolas, Suite 101\\
Montreal, Quebec, Canada, H2Y 2P5}
\date{\today}
\opening{Dear Sir or Madam,}
\closing{I have enclosed my CV for your consideration and I look forward to hearing from you shortly for an interview.}
\enclosure[Ci-joint]{curriculum vit\ae{}}

\makelettertitle

\textbf{Spontaneous application : Internship for Java Development}

\introduce{}
%%% COMPANY PART
I am requesting an internship in your firm \textit{Axon-ID} because I find the application for \textbf{Java Developer} very interesting on LinkedIn. During my year of studies in Chicoutimi, I studied a lot of advance tools in \textbf{Java} in order to design maintainable and flexible software. I worked on a cross-platform application dedicated to blind people, I designed it with the principles of Mobile Moment described by a Forester report. I choosed the framework \textbf{Ionic} for this application and I used \textbf{AngularJS} in order to build the logic of the application.
%%%

My three years of studies made me working on several considerable projects with a lot of programming language as \textbf{C++ or Python}. For example, I worked on a C++11 program in order to resolve the set covering problem thanks to metaheuristics and a simulator of an IRC chat with C++14 and Python (with PyQt) for a web serie called \textit{Toujours Vivant}. I enjoy being aware of the last advances of the C++ language and the STL library on the \textit{Hacker News} because I think these innovations will draw the new trends in software engineering. In addition to these projects, my engineer education is geared to the designing of architectures with UML and quality management for software development projects. As part of this course, I studied the upstream design of softwares by \textbf{designing UML models} and by \textbf{writing unit tests}. Furthermore, I have exercised a \textsc{scrum} team organisation for the prototyping of an android application which allows people to find recipes from products by scanning their barcode.

Moreover, during my second-year internship, I worked on a important 5-months project in Germany fully in English. This project was meant for the programming of a data viewer in C\#. We programmed the application from the prototype to the final software for the customer. I particulary worked on the logic and on the user interface of the application, this work made me familiar with the \textit{.NET Framework} and the \textit{MSDN}. I worked by myself on my personnal website which allows me to learn and practice JavaScript, HTML, CSS and Ruby languages. This website was an opportunity for me to build a personal project as a web developer. \conclude{}

\makeletterclosing
