\recipient{Canadian Tire Corporation}{
Kitchener, Ottawa\\
Canada}
\date{\today}
\opening{Madame, Monsieur,}
\closing{I have enclosed my CV for your consideration and I look forward to hearing from you shortly for an interview.}
\enclosure[Ci-joint]{curriculum vit\ae{}}

\makelettertitle

I am applying for an internship in your firm in order to acquire experience in software development, testing, and engineering knowledge. I know Canadian Tire as a big manufacturer in Canada and I would join your development team in order to help you to build the best software tools you need.

Currently, my three years of study in Computer Science engineering at ISIMA (College of Engineering in Computer Science, Modelling and Applications) and at the University of Québec in Chicoutimi led me to get interested in the \textbf{applications programming in Java and C++ and architectures of applications}. I have a sturdy luggage in software development and I hope improving my skills in your company. I am well aware of the UNIX operating system and I have already worked on CentOS, Ubuntu, Fedora, OpenSUSE and Linux Mint. Furthermore, I used to make a lot of scripts for bash in order to automate a lot of task on my computer. My previous internship in Infineon made me working on a C\# application and I needed to manage all the UI development, the logic of the application and the maintainability for the next teams on the project. I made my personal website and its development made me learn a lot of skills in web development, in addition to my work on a project dedicated to blind people \textit{blind.io}. I used Ionic framework and AngularJS in order to design a multiplatform application for a blind person who wishes to obtain help for the daily commute. I thought the architecture and the UI of the application.

My studies in the Software Engineering and Information Systems Division of ISIMA make me apt to work together with your company in the development of applications. As you see in my curriculum vit\ae{}, I am looking for a 6-month internship because I need it in order to validate my diploma but I am very flexible concerning the duration of the internship. I will be pleased to be able to discuss about your offer in an interview.

\makeletterclosing
