\recipient{CM Labs}{645 Wellington, \#301\\
Montreal, Quebec, H3C 1T2\\
Canada}
\date{\today}
\opening{Dear Sir or Madam,}
\closing{I have enclosed my CV for your consideration and I look forward to hearing from you shortly for an interview.}
\enclosure[Ci-joint]{curriculum vit\ae{}}

\makelettertitle

\textbf{Software Developer C++ in Montreal (Full-time)}

I am looking for an end-of-course internship in order to validate \textbf{my dual Master of Engineering from the French engineering school ISIMA and the university UQAC}. I am applying for your application in software development in order to practice my knowledge in C++ with your team. I have acquired this experience during my 3 years of studying in France and in Canada. I find that the CM Labs projects very interesting because of their match with my courses of \textit{simulation} and of \textit{metaheuristics} which sensibilise me to the significant impact of simulations in industry.

My three years of studies made me working on several considerable projects with a lot of programming language as \textbf{C++ or Python}. For example, I worked on a C++11 program in order to resolve the set covering problem thanks to metaheuristics and a simulator of an IRC chat with C++14 and Python (with PyQt) for a web serie called \textit{Toujours Vivant}. I enjoy being aware of the last advances of the C++ language and the STL library on the \textit{Hacker News} because I think these innovations will draw the new trends in software engineering. In addition to these projects, my engineer education is geared to the designing of architectures with UML and quality management for software development projects. As part of this course, I studied the upstream design of softwares by \textbf{designing UML models} and by \textbf{writing unit tests}. Furthermore, I have exercised a \textsc{scrum} team organisation for the prototyping of an android application which allows people to find recipes from products by scanning their barecode.

Moreover, during my second-year internship, I worked on a important 5-months project in Germany fully in English. This project was meant for the programming of a data viewer in C\#. We programmed the application from the prototype to the final software for the customer. This experience improved my skills in object-oriented programming and I wish to renew this within your team.

\makeletterclosing
