\recipient{Dell Computer Corp}{102 Chain Lake Dr\\
Halifax NS, B3S 1A7\\
Canada}

\date{\today}
\opening{Madame, Monsieur,}
\closing{I have enclosed my CV for your consideration and I look forward to hearing from you shortly for an interview.}
\enclosure[Ci-joint]{curriculum vit\ae{}}

\makelettertitle

I am applying for internship in your firm in order to acquire experience in software development, testing, and engineering knowledge. I know \textit{Dell} as one of the most influent provider of hardware solution for industry and people. I am really interesting in the application for working on a project devoted to helping non-profit organisation with their computing architecture management.

Currently, my three years of study in Computer Science engineering at ISIMA (College of Engineering in Computer Science, Modelling and Applications) and at the University of Québec in Chicoutimi led me to get interested in the \textbf{applications programming in Java and C++ and architectures of applications}. I have a solid luggage in software development and I hope improving my skills in your company. I worked on five student projects in C++ mainly for operational research and simulation. I follow with attention last news about C++ innovations and I have tried to familiarize me with these features in my last C++ project. In addition, I made two applications with Python 3. The first one is a tool devoted to managing the software NOMAD and the second one is a simulator of IRC conversation on terminal. My previous internship in Infineon made me work on a C\# application and I had to manage all the UI development, the logic of the application and the maintainability for the next teams on the project. Eventually, I have a solid background in the development of Object-Oriented software: I had an advance course of OOP where I experiment ideas in order to provide better program stable and easily maintainable.

My studies in the Software Engineering and Information Systems Division of ISIMA make me apt to work with your company in the development of applications. As you see in my curriculum vit\ae{}, I am applying for a 6-month internship because I need it in order to validate my diploma but I stay very flexible concerning the duration of the internship.

\makeletterclosing
