\recipient{Ericsson Canada Inc}{8400, boul Décarie, Mont-Royal \\
Montreal, Quebec, H4P 2N2\\
Canada}

\date{\today}
\opening{Madame, Monsieur,}
\closing{I have enclosed my CV for your consideration and I look forward to hearing from you shortly for an interview.}
\enclosure[Ci-joint]{curriculum vit\ae{}}

\makelettertitle

I am asking for an internship in your firm in order to acquire experience in software development, testing, and engineering knowledge. I know Ericsson as a great actor for the innovations in the ways of communication all over the world. Ericsson leads the improvement of the services linked to the network by making new infrastructures and new tools in order to design a global network faster, more accessible and easier to use. I find a lot of interests in the tools developed for your department \textit{Internet of Things} as the tool \textit{Calvin} or all your works dedicated to the \textit{WebRTC} features.

Currently, my three years of study in Computer Science engineering at ISIMA (College of Engineering in Computer Science, Modelling and Applications) and at the University of Québec in Chicoutimi led me to get interested in the \textbf{applications programming in Java and C++ and architectures of applications}. I have a sturdy luggage in software development and I hope improving my skills in your company. I developed some architecture tools in Java and AspectJ, and one of my study project is based on the study of the newest architectures, in order to improve the \textit{Apache Hadoop} architecture. In the same course, I made a study which compares two methods of architecture analysis. In addition I have an important experience of Python, I made an application which simulates an IRC conversation for a webserie and another one which automate an operational research software. My previous internship in Infineon made me working on a C\# application and I had to manage all the UI development, the logic of the application and the maintainability for the next teams on the project. Eventually, I had two courses about Oracle database: I know \textbf{the Oracle SQL and PL/SQL tools} that I used to manage the Oracle Cloud as a student.

My studies in the Software Engineering and Information Systems Division of ISIMA make me apt to work together with your company in the development of applications. As you see in my curriculum vit\ae{}, I am applying for a 6-month internship because I need it in order to validate my diploma but I stay very flexible concerning the duration of the internship.

\makeletterclosing
