\recipient{Houghton Mifflin Harcourt}{4200 Boulevard St. Laurent, Suite 1203\\
Montreal, QC H2W 2R2}
\date{\today}
\opening{Dear Sir or Madam,}
\closing{I have enclosed my CV for your consideration and I look forward to hearing from you shortly for an interview.}
\enclosure[Ci-joint]{curriculum vit\ae{}}

\makelettertitle

\textbf{Spontaneous application: Internship for Software Development}

\introduce{}
%%% COMPANY PART
I am requesting an internship as a spontaneous application in your firm \textit{Houghton Mifflin Harcourt} because you are a huge provider of learning solutions in America. Your opportunity of \textbf{Software Developer in Montréal} matches with my skills but I need one internship in order to validate my diploma. My last project was the development of my personal website where I experimented new web technologies and some design principles in order to create a website which matches with my personality. It was the opportunity for me to confirm my knowledge in \textbf{HTML, CSS, JavaScript and Ruby}.

My three years of studies made me working on several considerable projects with a lot of programming language as \textbf{C++ or Python}. For example, I worked on a C++11 program in order to resolve the set covering problem thanks to metaheuristics and a simulator of an IRC chat with C++14 and Python (with PyQt) for a web serie called \textit{Toujours Vivant}. I enjoy being aware of the last advances of the C++ language and the STL library on the \textit{Hacker News} because I think these innovations will draw the new trends in software engineering. In addition to these projects, my engineer education is geared to the designing of architectures with UML and quality management for software development projects. As part of this course, I studied the upstream design of softwares by \textbf{designing UML models} and by \textbf{writing unit tests}. Furthermore, I have exercised a \textsc{scrum} team organisation for the prototyping of an android application which allows people to find recipes from products by scanning their barcode.

Moreover, during my second-year internship, I worked on a important 5-months project in Germany fully in English. This project was meant for the programming of a data viewer in C\#. We programmed the application from the prototype to the final software for the customer. I particulary worked on the logic and on the user interface of the application, this work made me familiar with the \textit{.NET Framework} and the \textit{MSDN}. \conclude{}

\makeletterclosing
