\recipient{IBM Ottawa Lab}{2670 Queensview Drive\\
Ottawa, Ontario, K2B 8K1\\
Canada}
\date{\today}
\opening{Madame, Monsieur,}
\closing{I have enclosed my CV for your consideration and I look forward to hearing from you shortly for an interview.}
\enclosure[Ci-joint]{curriculum vit\ae{}}

\makelettertitle

I am applying for an internship in your firm in order to acquire experience in software development, testing, and engineering knowledge. I know IBM as a leader of innovation in computing technologies. As a student, I discovered your guidelines for design with IBM Design and I've tried to use the platform IBM Bluemix for a challenge of coding. In addition, I attended a lecture lead by Denis Gaudreault about the evolution of business with the latest innovations in computing.

Currently, my three years of study in Computer Science engineering at ISIMA (College of Engineering in Computer Science, Modelling and Applications) and at the University of Québec in Chicoutimi led me to get interested in the \textbf{applications programming in Java and C++ and architectures of applications}. I have a sturdy luggage in software development and I hope improving my skills in your company. I am well aware of the UNIX operating system and I have already worked on CentOS, Ubuntu, Fedora, OpenSUSE and Linux Mint. Furthermore, I used to carry out a lot of scripts for Bash in order to automate a lot of task on my computer. My previous internship in Infineon made me working on a C\# application and I needed to manage all the UI development, the logic of the application and the maintainability for the next teams on the project. II have studied project managment during my studies and I made an essay about the XP managment in firms. This essay made me really considerate about the importance of the test units processus and this point have been enhanced by the practice of tools as Valgrind, JUnit or CUnit Testing Framework. I also used Jenkins in an advance course of development and I have some interest about Circle Ci for my own project.

My studies in the Software Engineering and Information Systems Division of ISIMA make me apt to work together with your company in the development of applications. As you see in my curriculum vit\ae{}, I am looking for a 6-month internship because I need it in order to validate my diploma but I am very flexible concerning the duration of the internship. I will be pleased to be able to discuss about your offer in an interview.

\makeletterclosing
