\recipient{IBM Canada}{1250 René-Lévesque Boulevard\\
Montreal, Quebec, H3C 1T2\\
Canada}
\date{\today}
\opening{Madame, Monsieur,}
\closing{I have enclosed my CV for your consideration and I look forward to hearing from you shortly for an interview.}
\enclosure[Ci-joint]{curriculum vit\ae{}}

\makelettertitle

I am applying for an internship in your firm in order to acquire experience in software development, testing, and engineering knowledge. I know IBM as a leader of innovation in computing technologies. As a student, I discovered your guidelines for design with IBM Design and I've tried to use the platform IBM Bluemix for a challenge of coding. In addition, I attended a lecture lead by Denis Gaudreault about the evolution of business with the latest innovations in computing.

Currently, my three years of study in Computer Science engineering at ISIMA (College of Engineering in Computer Science, Modelling and Applications) and at the University of Québec in Chicoutimi led me to get interested in the \textbf{applications programming in Java and C++ and architectures of applications}. I have a sturdy luggage in software development and I hope improving my skills in your company. I am well aware of the UNIX operating system and I have already worked on CentOS, Ubuntu, Fedora, OpenSUSE and Linux Mint. Furthermore, I used to make a lot of scripts in Bash script in order to automate a lot of task on my computer. My previous internship in Infineon made me working on a C\# application and I needed to manage all the UI development, the logic of the application and the maintainability for the next teams on the project. All the UI of this application was made with WPF and I used all the principles of the MVVM specification. Eventually, I worked on my personal website and I learnt web programming by myself. I used JavaScript in another application for blind people I made for a course about the architecture of application for firms.

My studies in the Software Engineering and Information Systems Division of ISIMA make me apt to work together with your company in the development of applications. As you see in my curriculum vit\ae{}, I am looking for a 6-month internship because I need it in order to validate my diploma but I am very flexible concerning the duration of the internship. I will be pleased to be able to discuss about your offer in an interview.

\makeletterclosing
