\recipient{Optimal Payments}{Suite 700, 2 Place Alexis-Nihon\\
3500 de Maisonneuve Blvd. W.\\
Montreal, Quebec, H3C 1T2\\
Canada}
\date{\today}
\opening{Madame, Monsieur,}
\closing{I have enclosed my CV for your consideration and I look forward to hearing from you shortly for an interview.}
\enclosure[Ci-joint]{curriculum vit\ae{}}

\makelettertitle

I am requesting an internship in your firm in order to gain experience in software development, testing, and engineering knowledge. I know Optimal Payment as a provider of innovatives solutions for online and mobile payments. Your differents services made your customer's payments processing better by making them easier and more comfortable with the Internet and their mobile phone.

Currently, my three years of study in Computer Science engineering at ISIMA (College of Engineering in Computer Science, Modelling and Applications) and at the University of Québec in Chicoutimi led me to get interested in the \textbf{applications programming in Java and C++ and architectures of applications}. I have a sturdy luggage in software development and I hope improving my skills in your company. I developed some architecture tools in Java and AspectJ, and one of my study project is based on the study of the newest architectures, in order to improve the \textit{Apache Hadoop} architecture. I made studies about the framework \textbf{Spring} and more precisly in the advantages and drawbacks of the MVC architecture. My previous internship in Infineon made me working on a C\# application and I needed to deal with all the UI development, the logic of the application and the maintainability for the next teams on the project. Eventually, I had two courses about Oracle database: I know \textbf{the Oracle SQL and PL/SQL tools} that I used to practice them on the Oracle Cloud as a student.

My studies in the Software Engineering and Information Systems Division of ISIMA make me apt to work together with your company in the development of applications. As you see in my curriculum vit\ae{}, I am looking for a 6-month internship because I need it in order to validate my diploma but I am very flexible concerning the duration of the internship. I will be pleased to be able to discuss about your offer in an interview.

\makeletterclosing
