\recipient{Orckestra Inc}{
Montreal, Quebec,\\
Canada}

\date{\today}
\opening{Madame, Monsieur,}
\closing{I have enclosed my CV for your consideration and I look forward to hearing from you shortly for an interview.}
\enclosure[Ci-joint]{curriculum vit\ae{}}

\makelettertitle

I am applying for an internship in your firm in order to acquire experience in software development, testing, and engineering knowledge. I know Orckestra as a provider of solutions for e-commerce and I would join your development team in order to help you to build the best software tools you need.

Currently, my three years of study in Computer Science engineering at ISIMA (College of Engineering in Computer Science, Modelling and Applications) and at the University of Québec in Chicoutimi led me to get interested in the \textbf{applications programming in Java and C++ and architectures of applications}. I have a sturdy luggage in software development and I hope improving my skills in your company. I developed some architecture tools in Java and AspectJ, and one of my study project is based on the study of the newest architectures, in order to improve the \textit{Apache Hadoop} architecture. In the same course, I got a lot of interest in the development of a mobile software architecture dedicated to blind people. I made studies about the framework \textbf{Spring} and more precisly in the advantages and drawbacks of the MVC architecture. My previous internship in Infineon made me working on a C\# application and I had to manage all the UI development, the logic of the application and the maintainability for the next teams on the project. I worked on a project which was designed to allow people to find recipes directly from a picture of their fridge and I enjoyed making all the software architecture.

My studies in the Software Engineering and Information Systems Division of ISIMA make me apt to work together with your company in the development of applications. As you see in my curriculum vit\ae{}, I am applying for a 6-month internship because I need it in order to validate my diploma but I stay very flexible concerning the duration of the internship.

\makeletterclosing
